Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
improved

The 25 most frequently used codewords in the test set are shown in
Figure \ref{fig:codes1}.  
The frequency of use of these codewords are shown in Figure \ref{fig:freqs}.
The codewords primarily consist of sustained
notes and simple chords.  Since they are designed to be key-invariant,
specific notes do not appear.  Instead the first 7 codewords
correspond to a single note sustained across two bars (codeword 0),
perfect fifth (codewords 1 and 2) and fourth intervals (codewords 3
and 6), and a
major and minor triads (codewords 5 and 4, respectively).  Many of the remaining
codewords correspond to common transitions from one chord to another,
\eg a transitions between major triads in codes 7 and 9 ( Cmaj
$\rightarrow$ Fmaj)% assuming that chroma 0 is C) 
and the reverse transition in code 21 (\ie Fmaj $\rightarrow$ Cmaj).
FIXME: Does this transition have a better name like ``relative x''?

@@

Showing codewords of $2$ bars is practical and consistent with our experiments
in Section \ref{sec:exps2}. However, longer codewords can also reveal
interesting structure. A random sample of such codewords is presented
in Figure \ref{fig:codes8bars}.  FIXME: why a random sample?  Can we
show their usage in the test (or train) set as in fig \ref{fig:codes1}?

>>>>

The 25 most frequently used codewords in the test set are shown in
Figure \ref{fig:codes1}.  
The frequency of use of these codewords are shown in Figure \ref{fig:freqs}.
The codewords primarily consist of sustained
notes and simple chords.  Since they are designed to be key-invariant,
specific notes do not appear.  Instead the first 7 codewords
correspond to a single note sustained across two bars (codeword 0),
perfect fifth (codewords 1 and 2) and fourth intervals (codewords 3
and 6), and a
major and minor triads (codewords 5 and 4, respectively).  Many of the remaining
codewords correspond to common transitions from one chord to another,
\eg a transitions between major triads in codes 7 and 9 ( Cmaj
$\rightarrow$ Fmaj or C5 $\rightarrow$ F5 as a guitar power chord)
% assuming that chroma 0 is C) 
and the reverse transition in code 21 (\ie Fmaj $\rightarrow$ Cmaj).
%FIXME: Does this transition have a better name like ``relative x''?
% C5 -> F5 in 'guitar chords', basically a power chord

@@

Showing codewords of $2$ bars is practical and consistent with our experiments
in Section \ref{sec:exps2}. However, longer codewords can also reveal
interesting structure. A random sample of such codewords is presented
in Figure \ref{fig:codes8bars}. Most used codewords would be less interesting,
as they all are sustained patterns.
